Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-14 paper/main.tex
reads over conclusion

This manuscript has explored the performance of \numberofstrategies strategies
of the Iterated Prisoner's Dilemma in a large number of computer tournaments.
We analyzed and extracted the salient features of the best performing strategies
across various tournament types, casting the results in terms of Axelrod's
original suggested features of good IPD strategies. Moreover, our results
shed light on the historic performance of TFT, zero-determinant strategies,
and memory one strategies generally. Strategies need to match their play
to the cooperativeness of the tournament population and do so in a way that
prevents or minimizes exploitation. Overall we see that complex or clever
strategies can be effective, whether trained against a corpus of possible
opponents or purposely designed to mitigate the impact of noise such as
in the strategy DBS. Further, we showed that while the type of exploitation
attempted by ZDs is not typically effective in tournaments, more
sophisticated strategies capable of selectively exploiting weaker opponents
while mutually cooperating with stronger opponents can be highly successful.
This fact was also indicated numerically by the importance of the strategy
feature SSE in the analysis of strategy features. These results highlight
a central idea in evolutionary game theory in this context: the fitness
landscape is a function of the population (where fitness in this case is
tournament performance). While that may seem obvious now, it shows why
historical tournament results on small or arbitrary populations of strategies
have so often failed to produce generalizable results.

@@

Furthermore, in Section~\ref{section:top_performances}
and~\ref{section:evaluation_of_performance} it was shown that envious strategies
performed well. Though these were not the most envious strategies in the
tournaments (ZDs were included), these strategies benefited by being a bit
envious. From Section~\ref{section:evaluation_of_performance} it was concluded
that there is a significant importance in adapting to the environment, and more
specifically in this work, to the mean cooperator. This section also
demonstrated that a strategy should reciprocate, as suggested by Axelrod, but in
some environments, such as standard and noisy, it should relax its readiness to
do so.

@@

\begin{itemize}
\item be nice, if the environment isn't noisy and the games are long
    \item be provocable and contrite, 
    \item be a little envious, 
    \item it's ok to be clever, 
    \item adapt to the environment (including the population of strategies).
\end{itemize}

>>>>

This manuscript has explored the performance of \numberofstrategies strategies
of the IPD in a large number of computer tournaments.
We analyzed and extracted the salient features of the best performing strategies
across various tournament types, casting the results in terms of R. Axelrod's
original suggested features of good IPD strategies. Moreover, our results
shed light on the historic performance of TFT, zero-determinant strategies,
and memory-one strategies generally. Strategies need to match their play
to the cooperativeness of the tournament population and do so in a way that
prevents or minimizes exploitation. Overall we see that complex or clever
strategies can be effective, whether trained against a corpus of possible
opponents or purposely designed to mitigate the impact of noise such as
in the strategy DBS. Further, we showed that while the type of exploitation
attempted by ZDs is not typically effective in tournaments, more
sophisticated strategies capable of selectively exploiting weaker opponents
while mutually cooperating with stronger opponents can be highly successful.
This fact was also indicated numerically by the importance of the strategy
feature SSE in the analysis of strategy features. These results highlight
a central idea in evolutionary game theory in this context: the fitness
landscape is a function of the population (where fitness in this case is
tournament performance). While that may seem obvious now, it shows why
historical tournament results on small or arbitrary populations of strategies
have so often failed to produce generalizable results.

@@

Furthermore, in Section~\ref{section:top_performances}
and~\ref{section:evaluation_of_performance} it was shown that envious strategies
performed well. Though these were not the most envious strategies in the
tournaments (ZDs were included), these strategies benefited by being a bit
envious. From Section~\ref{section:evaluation_of_performance} it was concluded
that there is a significant importance in adapting to the environment, and more
specifically in this work, to the mean cooperator. This section also
demonstrated that a strategy should reciprocate, as suggested by R. Axelrod, but in
some environments, such as standard and noisy, it should relax its readiness to
do so.

@@

\begin{itemize}
\item be nice, if the environment isn't noisy and the games are long
    \item be provocable and forgiving,
    \item be a little envious,
    \item it's ok to be clever,
    \item adapt to the environment (including the population of strategies).
\end{itemize}
